\input{shared/ietf-slides.tex}

\title{CoAP: Non-traditional response forms}
\subtitle{\ietfdraft{bormann-core-responses-02}}
\author{Carsten~Bormann, \textit{Christian~Amsüss}}
\date{2024-03-20 \\CoRE at IETF 119 in Brisbane}

\begin{document}

\frame{\titlepage}

\begin{frame}{Non-traditional responses}\Large
    \begin{block}{Non-traditional response}
    A response that is not the single response
    generated for a request received on the same transport.
    \end{block}

    \begin{itemize}
        \item Define new versatile non-traditional responses
        \item \textit{Define behavior of non-traditional responses in general}
    \end{itemize}
\end{frame}

\begin{frame}{Behavior definition: OSCORE}\Large
    \framesubtitle{New in -02}

    \begin{itemize}
        \item Explicit request or not: Request needs sender and sequence number.
        \item Request nonce can only be used in one response.
        \item If order matters, responses are ordered by sequence number.
        \item If replaying matters, responses are subjected to the replay window.
        \item If follow-up requests were made, transiently tolerate erroneous responses.
    \end{itemize}

    \bigskip

    \ldots and that's it on the OSCORE side?
\end{frame}

\begin{frame}{Next steps}\Large
    \begin{itemize}
        \item Interop based on concrete documents adopting this?
        \item Future in the WG?
    \end{itemize}
\end{frame}

\begin{frame}{Backup slide: Potential users}
\framesubtitle{Adapted from IETF113 slide set}

\begin{description}[RFC7252 simplest case]
% 2010 
\item[\color{gray}RFC7252 simplest case] {\color{gray} Single request, single response}

% 2010 
\item[RFC7252 multicast] Single request, different responses with different source addresses

% 2010
\item[RFC7641] Observe notifications come in until further notice\footnote{No intent to redefine, but implementers may use common mechanisms}

% 2011
\item[core-coap-sms] Response-To-Uri-Host/-Port -- triangular requests

% 2013
\item[core-coap-endpoint-id] Observations across server address changes

% 2017
\item[core-responses-00] Configured requests, Response-For

% 2020
\item[RFC9177] Responding with multiple blocks

% 2020
\item[core-groupcomm-proxy] Multicast-Timeout
\end{description}
\end{frame}

\end{document}
